Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-19 WSSSPE2_report/WSSSPE2_review.tex
Absract: line breaks.
Abstract: change one word.
updated abstract

\begin{abstract}      
\todo{update abstract}
This technical report records and discusses the alternative submission and peer-review process used by
the Second Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE2) and the results of that process. It is intended to record
both the program-organization model adapted by WSSSPE2
as well as the papers accepted by the workshop.
\end{abstract}

>>>>

\begin{abstract}      
This technical report records and discusses the Second Workshop on Sustainable Software for
Science: Practice and Experiences (WSSSPE2).  The workshop used an alternative submission
and peer-review process, which led to a set of papers divided across five topic areas:
exploring sustainability;
software development experiences;
credit \& incentives;
reproducibility \& reuse \& sharing; and
code testing \& code review.
The report includes a description of the submission and review process, the workshop
keynote presentations,
a discussion on sustainability, and the five discussions from the topic areas.  The report also
contains a description of potential actions that were proposed in the the five discussions.
\end{abstract}
